Online Source Code Reuse: A Case Study of Stackoverflow \textit{vs.~}Qualitas OSS

### 2016-07-24 latex/stackoverflow.tex
Updated after finishing analysing 528 ok pairs (fixed some problems)

\section*{Agreed Cloned Fragments}
The results from both tools are compared to find clone pairs that they mutually agree.  Theses agreed clone pairs will be manually investigated. The results of agreed clone pairs found by different parameter settings of Simian and NiCad are shown in Table \ref{t_agreed_clone}.

\begin{table}[h]
	\centering
	\caption{Agreed cloned fragments between Simian and Nicad}
	\label{t_agreed_clone}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 92          & 1        \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 155         & 25           \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

Relationships between the cloned fragments are displayed in Fig.~\ref{fig:venn4}.

\begin{figure}[H]
\centering
\includegraphics[width=0.5\linewidth]{venn4}
\caption[Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings]{Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings}
\label{fig:venn4}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{venn4_pairs}
	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
	\label{fig:venn4_pairs}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Classification results of 14 \textit{good} and 183 \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
	\label{tab:classification}
		\begin{tabular}{|l|r|r|r|r|r|r|r|}
			\hline 
			Classification & A & B & C & D & E & F & Total \\ 
			\hline 
		    \multirow{2}{*}{\textit{good-match(0.7)}} & 1 & 2 & 2 & 2 & 7 & 0 & 14 \\ \cline{2-8}
			 & 7.14\%	& 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
			\hline
			\multirow{2}{*}{\textit{ok-match(0.7) - strict}} & 2 & 2 & 2 & 21 & 146 & 10 & 183 \\ \cline{2-8}
			& 1.09\%	& 1.09\%	&	1.09\%	&	11.48\%	&	79.78\%	&	5.46\%	&	100.00\%  \\ 
			\hline
			\multirow{2}{*}{\textit{ok-match(0.7) - loose}}  & 1 & 2 & 2 & 20 & 48 & 9 & 82 \\ \cline{2-8}
			& 1.22\%	&	2.44\%	&	2.44\%	&	24.39\%	&	58.54\%	&	10.98\%	&	100.00\% \\
			\hline 
		\end{tabular} 
\end{table}

>>>>

%\section*{Agreed Cloned Fragments}
%The results from both tools are compared to find clone pairs that they mutually agree.  Theses agreed clone pairs will be manually investigated. The results of agreed clone pairs found by different parameter settings of Simian and NiCad are shown in Table \ref{t_agreed_clone}.

%\begin{table}[h]
%	\centering
%	\caption{Agreed cloned fragments between Simian and Nicad}
%	\label{t_agreed_clone}
%	\begin{tabular}{l|r|r}
%		\hline
%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		NiCad$_{\mathrm{\textit{default}}}$ & 92          & 1        \\%      & 709             \\
%		NiCad$_{\mathrm{\textit{fse13}}}$   & 155         & 25           \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

%Relationships between the cloned fragments are displayed in Fig.~\ref{fig:venn4}.

%\begin{figure}[H]
%\centering
%\includegraphics[width=0.5\linewidth]{venn4}
%\caption[Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings]{Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings}
%\label{fig:venn4}
%\end{figure}

@@

\section*{Duplicated Agreed Clone Pairs}

\begin{table}[H]
	\centering
	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
	\label{t_dup_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r|r|r}
		\hline
		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		$S_dN_d$ & 9 & 3 & 0 & 0 \\%      & 709             \\
		$S_dN_f$ & 3 & 3 & 0 & 0 \\ % & 4680            \\
		$S_fN_d$ & 0 & 0 & 1 & 1 \\
		$S_fN_f$ & 0 & 0 & 1 & 5 \\	
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
	\label{fig:venn4_pairs}
\end{figure}

\begin{table}[h]
	\centering
	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings}
	\label{t_dup_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r|r|r}
		\hline
		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		$S_dN_d$ & 373 & 17 & 0 & 0 \\%      & 709             \\
		$S_dN_f$ & 17 & 118 & 0 & 0 \\ % & 4680            \\
		$S_fN_d$ & 0 & 0 & 1 & 1 \\
		$S_fN_f$ & 0 & 0 & 1 & 36 \\	
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
	\label{fig:venn4_pairs}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Classification results of 14 \textit{good} and 183 \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
	\label{tab:classification}
		\begin{tabular}{|l|r|r|r|r|r|r|r|}
			\hline 
			Classification & A & B & C & D & E & F & Total \\ 
			\hline 
		    \multirow{2}{*}{\textit{good-match(0.7)}} & 1 & 2 & 2 & 2 & 7 & 0 & 14 \\ \cline{2-8}
			 & 7.14\%	& 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
			\hline
			\multirow{2}{*}{\textit{ok-match(0.7)}} & 4 & 42 & 8 & 351 & 28 & 77 & 510 \\ \cline{2-8}
			& 0.78\%	& 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
			\hline
		\end{tabular} 
\end{table}
